I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-17 Paper/proofs.tex
proof update

				%	 \item $w_{b,z}=0$, or
				%	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.

@@

			%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.

@@

			%	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
			%	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.

@@

			%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).

@@

			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
			%of its (LP) approximation if $w_{b,z}<0$. 

@@

			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 

@@

			%and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
			%	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).

@@

			%$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.

@@

			%$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$

@@

			%For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$

@@

			%$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
			%=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))

@@

				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be on a weak compensating pair if and only if one of the following two happens:
					\begin{enumerate}
						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $w_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $w_{a_j,b}=0$ to denote this case.
					\end{enumerate}

@@

				\begin{proof}
					First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.

					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
					Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
					Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
					from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
					Then $((a_j,b,z), \pi')$ is also a weak compensating pair.
				\end{proof}

@@

					1. if $b\in J$, by definition, $w_{bc}=0$.

					2. if $b\in B_{open}$, then $w_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.

					3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
				\end{proof}

@@

				%\begin{lemma}\label{lem:pure_node}
				%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
				%\end{lemma}
				%
				%\begin{proof}
				%	We prove this lemma by induction. For the first hidden layer, this is trivial.
				%	
				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 +\sum_{b\in B_{zero}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
				%	
				%	
				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $w_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $w_{bc}=0$. Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
				%\end{proof}

@@

				\begin{lemma}
					For any node $c$ in a hidden layer or the output layer, if $c\notin B_{zero}$, then:		\begin{enumerate}
						\item for any fixed $\boldsymbol{x}^0_J$, when  $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$. The same is true for $\boldsymbol{x}^\sharp_I$.

@@

					(2) If $S(c)=1$, then we have the following:	\begin{align*}
						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$. Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
						&constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
						= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
					\end{align*}  This is the first equal.

					The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}. $S(c)=-1$ is similar. So we have proved part 2.

					(3) Once we have part 2, then we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$. Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$. This is what we want to show, and the same result holds for lower bound and minimal value. This is for part 3.

@@

@@

				%\vspace*{20ex}
				%\begin{proof}
				%	
				%	For $i= 1$, we have proved in previous section.
				%	
				%	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
				%	
				%	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
				%	
				%	\begin{align*}
					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$. $\B$ is one of $\UB,\LB$  that, if $w_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
				%	
				%	We can simplify above equation to \begin{align*}
					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*}
				%	
				%	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
					%		 &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
					%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
					%	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
				%	
				%Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$. Hence, by induction hypothesis, we will have \begin{align*}
					%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
					%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
					%\end{align*} This finishes the proof.
					%	\end{proof}
				%
				%
				%Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$. Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$. This is what we want to show, and the same result holds for lower bound and minimal value.

>>>>

				%	 \item $W_{b,z}=0$, or
				%	 \item For every input node $j\in J$, we have $W_{a_j,b}=0$.

@@

			%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.

@@

			%	Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
			%	Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.

@@

			%	$$b= B^0 +\sum_{a_i\in I} W_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}W_{b_ha_i}+B_h$ ($B_h$ is the bias). 

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).

@@

			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $W_{b,z}>0$, and the lower bound
			%of its (LP) approximation if $W_{b,z}<0$. 

@@

			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(W_{zb})=1$, then 

@@

			%and if $S(b)=\mathrm{sign}(W_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
			%	\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).

@@

			%$W_{b,z} = 0$ and $b \in B^2$ iff $W_{b,z} \neq 0$.

@@

			%$$\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$

@@

			%For $b \in B^2$, we have $W_{a_j,b}=0$ for all $j \in J$

@@

			%$$\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
			%=\sum_{b\in B^2} W_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))

@@

				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}W_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be on a weak compensating pair if and only if one of the following two happens:
					\begin{enumerate}
						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
					\end{enumerate}

@@

				\begin{proof}
					First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.

					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
					Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
					Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
					from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
					Then $((a_j,b,z), \pi')$ is also a weak compensating pair.
				\end{proof}

@@

					1. if $b\in J$, by definition, $W_{bc}=0$.

					2. if $b\in B_{open}$, then $W_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.

					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
				\end{proof}

@@

				%\begin{lemma}\label{lem:pure_node}
				%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
				%\end{lemma}
				%
				%\begin{proof}
				%	We prove this lemma by induction. For the first hidden layer, this is trivial.
				%	
				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 +\sum_{b\in B_{zero}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
				%	
				%	
				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $W_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $W_{bc}=0$. Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
				%\end{proof}

@@

				\begin{lemma} \label{lem:main}
					For any node $c$ in a hidden layer or the output layer, if $c\notin B_{zero}$, then:		\begin{enumerate}
						\item for any fixed $\boldsymbol{x}^0_J$, when  $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$. The same is true for $\boldsymbol{x}^\sharp_I$.

@@

					(2) If $S(c)=1$, then we have the following:	\begin{align*}
						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$. Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.

					Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$. Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same sign. And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions. Combining all these facts, we have:\begin{align*}
						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
						&constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
						= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
					\end{align*}  This is the first equal.

					The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}. The case $S(c)=-1$ is similar. This is for part 2.

					(3) Once we have part 2, we will have that for any fixed $\boldsymbol{x}^0_J$, $$\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c).$$ Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)$ and this is to say $\UB(c)=\max(c)$. This is what we want to show, and the same result holds for lower bound and minimal value. This is for part 3. \qed

@@

				From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{th2}.

@@

				%\vspace*{20ex}
				%\begin{proof}
				%	
				%	For $i= 1$, we have proved in previous section.
				%	
				%	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
				%	
				%	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
				%	
				%	\begin{align*}
					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$. $\B$ is one of $\UB,\LB$  that, if $W_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
				%	
				%	We can simplify above equation to \begin{align*}
					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*}
				%	
				%	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
					%		 &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
					%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
					%	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
				%	
				%Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$. Hence, by induction hypothesis, we will have \begin{align*}
					%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
					%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
					%\end{align*} This finishes the proof.
					%	\end{proof}
				%
				%
				%Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$. Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$. This is what we want to show, and the same result holds for lower bound and minimal value.
